Computer Science House By-Laws

### 2016-05-23 bylaws.tex
Collect dues whenever, just not after Evals

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
At the start of the academic year, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected at the start of each semester by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\bsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

>>>>

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\\*\\*
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
\bsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}
